Abstract Data Type Inference

### 2015-03-24 nature.tex
Register histories typo.

Our inference algorithm computes following four histories to generate the
complement of the atomic register ADT:
\begin{verbatim}
  [1:X] read => 1 (RO)  #          [1:2] read => 1 (RO)  #
  ---                              [2:2] write(1)          #
  [1:1] write(1)            #      ---
  [2:2] read => empty (RO)    #    [1:1] write(1)        #
\end{verbatim}
As new generators are discovered for $n=1$ and $n=2$ matches only, the atomic
register ADT is predictable.

>>>>

Our inference algorithm computes following four histories to generate the
complement of the atomic register ADT:
\begin{verbatim}
  [1:X] read => 1 (RO)  #        [1:1] write(1)        #
  ---                            [2:2] read => - (RO)    #
  [1:1] write(1)        #        ---
  [2:2] write(2)          #      [1:2] read => 1 (RO)  #
  [3:1] read => 1 (RO)      #    [2:2] write(1)          #
\end{verbatim}
As new generators are discovered for $n=1$ and $n=2$ matches only, the atomic
register ADT is predictable.
